Higher-Order unification for free!

### 2024-04-12 paper/main.tex
sec 2.4 with spellchecker

\noindent
An example of term \maybebeta{} is the application $F \appsep x$.
This term is problematic since the application node of
its syntax tree cannot be used to justify a
unification failure, i.e. by properly instantiating $F$ the term
head constructor may become a $\lambda$, or a constant or stay an application.

@@

\noindent
An example of term $s$ in \maybeeta{} is
$\lambda x.\lambda y.F \appsep y \appsep x$
since the substitution
$\rho = \{ F \mapsto \lambda a.\lambda b.f \appsep b \appsep a\}$
makes $\rho s = \lambda x.\lambda y.f \appsep x \appsep y$
that is the eta long form of $f$. This term is problematic since
its leading $\lambda$ abstraction cannot justify a
unification failure against a constant $f$.

@@

\noindent
These terms are problematic for the very same reason terms in \maybebeta are,
but cannot be handled directly by the unification of the meta language, that
is only required to handle terms in \llambda. Still, there exists a
substitution $\rho$ such that $\rho s \in \llambda$.

@@

\noindent
Proposition \ref{prop:w-preservation} is key to prove \cref{prop:simulation,prop:fidelity}:
informally it says that the problematic terms moved on the side by the compiler
are not put back by \hstep, hence \Ue{} can continue to operate properly.
In \cref{sec:simulation,sec:eta,sec:beta}
we describe how the compiler recognizes terms in \maybebeta, \maybeeta and
\notllambda and how \progress takes care of them preserving \wellb
and granting \cref{prop:simulation,prop:fidelity,prop:fidelity-recovery}.

>>>>

\noindent
An example of a \maybebeta{} term is the application $F \appsep x$.
This term is problematic since the application node of
its syntax tree cannot be used to justify a
unification failure, i.e. by properly instantiating $F$ the term
head constructor may become a $\lambda$, or a constant, or remain an application.

@@

\noindent
An example of a term $s$ in \maybeeta{} is
$\lambda x.\lambda y.F \appsep y \appsep x$
since the substitution
$\rho = \{ F \mapsto \lambda a.\lambda b.f \appsep b \appsep a\}$
makes $\rho s = \lambda x.\lambda y.f \appsep x \appsep y$,
which is the eta long form of $f$. This term is problematic since
its leading $\lambda$ abstraction cannot justify a
unification failure against a constant $f$.

@@

\noindent
These terms are problematic for the very same reason terms in \maybebeta are,
but they cannot be handled directly by the unification of the meta language, which
is only required to handle terms in \llambda. Still, there exists a
substitution $\rho$ such that $\rho s \in \llambda$.

@@

\noindent
Proposition \ref{prop:w-preservation} is key to proving \cref{prop:simulation,prop:fidelity}.
Informally, it says that the problematic terms moved on the side by the compiler
are not reintroduced by \hstep, hence \Ue{} can continue to operate properly.
In \cref{sec:simulation,sec:eta,sec:beta}
we describe how the compiler recognizes terms in \maybebeta, \maybeeta and
\notllambda and how \progress takes care of them preserving \wellb
and ensuring \cref{prop:simulation,prop:fidelity,prop:fidelity-recovery}.
